Viscous Transport in Eroding Porous Media

### 2019-05-15 docs/transport/erosion_transport.tex
do the result section in transport paper

\author[SH]{Shang-Huan Chiu}
\author[Nick]{M.~N.~J.~Moore}
\author[Bryan]{Bryan D.~Quaife}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}.
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

Besides the channels between two bodies, there is a single channel

>>>>

\author[SH]{Shang-Huan Chiu}
\author[Nick]{M.~Nicholas J.~Moore}
\author[Bryan]{Bryan D.~Quaife}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}.
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

Besides the channels between two bodies, there is a single channel across from left to right of the domain and the flow has been concentrated in this channel. In the second frame of Fig.~\ref{fig:Eroding20vort}, this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. We can get a better understanding from the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
the flow (or tracer) first comes from three small channels between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become one main channel between bodies 1 \& 9. After
